|

### 2020-11-25 02-Chp2-Background.Rmd
Small starter fixes

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

# Background {#background-heading}

>>>>

# Background {#background-heading}
\minitoc <!-- this will include a mini table of contents-->

### 2020-11-25 03-Chp2-Systematic-Review.Rmd
Small starter fixes

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2:  
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

# Chapter 2: Systematic Review {#sys-rev-heading}
\minitoc <!-- this will include a mini table of contents-->

>>>>

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

# Systematic Review {#sys-rev-heading}
\minitoc <!-- this will include a mini table of contents-->

### 2020-11-25 index.Rmd
Small starter fixes

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: none 
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    output_dir: "docs"
    split_bib: false
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    output_dir: "docs"
    toc: true
    toc_depth: 2
    reference_docx: templates/word-styles-reference-01.docx   
link-citations: true
documentclass: book

>>>>

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: default 
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    output_dir: "docs"
    split_bib: false
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    output_dir: "docs"
    toc: true
    toc_depth: 2
    reference_docx: templates/word-styles-reference-01.docx   
link-citations: true
documentclass: book
